---
title: "Tibble tutorial"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: >
  Tutorial covering the tibble 
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(mgrtibbles)
knitr::opts_chunk$set(echo = FALSE)
```


## Tibbles

### Overview

A __tibble__ (`tbl`) is a reimagining of the __data.frame__ (`df`) object. They are described as __data.frames__ that are:

- __Lazy__: They don’t change variable names and they partial matching does not work.
- __Surly__: They complain more such as when a variable does not exist.

One important note is that __tibbles__ don’t have row names.

Although __tibbles__ have advantages compared to __data.frames__ they are not always more suited to the task than __data.frames__. 
However, __tibbles__ are generally always preferred over __data.frames__ when using __tidyverse__ packages.

### Tibble example

Run the below code for an example of:

- Creating a basic tibble
- Printing the tibble

```{r tbl-example, exercise=TRUE, exercise.eval=FALSE}
#Create a tibble
tbl <- tibble::tibble(Day = c("Mon", "Tue", "Wed"),
              Hawks = c(3,7,2),
              Pigeons = c(52,21,61),
              Starlings = c(1,2,1))
#Print tibble
tbl
```

###

Other text

###

Next piece

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

